Response to the defense feedback

### 2021-06-19 Chapter-5/Chapter-5.tex
Updates from Overleaf

\section{Implementation}
We have implemented a prototype of \ctool{}. It takes an input of ELF binary as well as the source code of the corresponding program. The front-end of \ctool{} is implemented in Python. It can generate random inputs and test the program with these inputs many times.  The address recording part is implemented as an Intel Pin tool plugin in C++ to record the bitmap for each input. The main component uses \textsf{libelfin}, an open-source library to parse ELF binaries and read DWARF debug information. The current implementation can support  64-bits ELF binary in Linux.

@@

Table~\ref{chapter5:table:over_result} presents the overview result. The minimum unit of the program during the experiment is one function. If a function has more than one access bitmap, then the function is vulnerable to side-channel attacks. We measure the side-channel leakages at two different granularities: the byte level and the cache line level. The result shows that programs have more vulnerable functions and tend to leak more information at the byte level than the cache line level. We run the target program under random inputs and record memory accesses. For cryptography programs, we run the target program with $4096$ different inputs. During the fuzzing process, if the program does not have a new memory access bitmap after several rounds, we call the fuzzing step is fixed. From the side-channel detection aspect, it is not necessary to continue running the experiments since more rounds do not reveal new leakages. During the experiment, we find AES ciphers reach the fixed point after about $300$ rounds, and RSA can reach the fixed point after around $500$ rounds. Previous work~\cite{217537} also reported a similar result. We continue running the experiment during our experiment until the observed value for the same observation is at least $5$ to satisfy the chi-square test requirement. Therefore, we choose to run all the cipher with different inputs for $4096$ times.  If one program has more than two leaked functions, we run the chi-squared test and calculate the total amount of leakages.

\subsection{Cryptography Libraries}
AES encryption can be divided into three steps. In the first step, the round keys are derived from the encryption keys (AES key schedule), and a state array is initialized with the plain-text and the initial round step. In the second step, the AES performs eleven rounds of state manipulation. In the final stage, the state array is copied out as the encrypted data.
The reference implementation uses lookup tables in the first two steps. Intuitively, the implementation is vulnerable to side-channel attacks. There are some mitigated versions of AES. We evaluate \ctool{} on three variants of AES implementations: the reference implementation, the bit-sliced version, and the AES-NI implementation.
For mebedTLS, we evaluate AES-NI and the reference implementation. We do not find any leakage sites in the AES-NI version. On the other hand, the reference implementation has several leakage sites. The bit-sliced version from OpenSSL and wolfSSL should be resistant to side-channel attacks. However, we find they only adopt the protection in the encryption function but leave the key expansion function unprotected. The T-Table implementation has side-channel leakage sites in both the key expanding function and the actual encryption function.

The RSA implementations blind the secret data on a random value before operating on it. We use a fixed RSA blinding value to avoid non-deterministic behaviors during the execution. After that, we compare the result with the previous work~\cite{bao2021abacus,203878}. The result shows that \ctool{} can identify all leakage sites reported in the previous work. In addition, \ctool{} identifies new leakages in the private key decode function (\textsf{conv\_ascii2bin}) in OpenSSL 1.1.1.  To evaluate the effectiveness of the quantification result, we compare the two RSA implementations between OpenSSL 1.1.0 and OpenSSL 1.1.1.  We are interested if these leaked functions in OpenSSL 1.1.0 are fixed in OpenSSL 1.1.1.
Note that \ctool{} can analyze the side-channel leakages at both the byte granularity and the cache line granularity. We show the result analyzed with cache line granularity.

>>>>

\section{Implementation}
We have implemented a prototype of \ctool{}. It takes an ELF binary as well as the source code of the corresponding program. The front-end of \ctool{} is implemented in Python. It can generate random inputs and test the program with these inputs many times.  The address recording part is implemented as an Intel Pin tool plugin in C++ to record the bitmap for each input. The main component uses \textsf{libelfin}, an open-source library to parse ELF binaries and read DWARF debug information. The current implementation can support  64-bits ELF binary in Linux.

@@

Table~\ref{chapter5:table:over_result} presents the overview result. The minimum unit of the program during the experiment is one function. If a function has more than one access bitmap, then the function is vulnerable to side-channel attacks. We measure the side-channel leakages at two different granularities: the byte level and the cache line level. The result shows that programs have more vulnerable functions and tend to leak more information at the byte level than the cache line level. We run the target program under random inputs and record memory accesses. For cryptography programs, we run the target program with $4096$ different inputs. During the fuzzing process, if the program does not have a new memory access bitmap after several rounds, we call the fuzzing step reaches a fixed point. From the side-channel detection aspect, it is not necessary to continue running the experiments since more rounds do not reveal new leakages. During the experiment, we find AES ciphers reach the fixed point after about $300$ rounds, and RSA can reach the fixed point after around $500$ rounds. Previous work~\cite{217537} also reported a similar result. We continue running the experiment during our experiment until the observed value for the same observation is at least $5$ to satisfy the chi-square test requirement. Therefore, we choose to run all the cipher with different inputs for $4096$ times.  If one program has more than two leaked functions, we run the chi-squared test and calculate the total amount of leakages.

\subsection{Cryptography Libraries}
AES encryption can be divided into three steps. In the first step, the round keys are derived from the encryption keys (AES key schedule), and a state array is initialized with the plain-text. In the second step, the AES performs eleven rounds of state manipulation. In the final stage, the state array is copied out as the encrypted data.
The reference implementation uses lookup tables in the first two steps. Intuitively, the implementation is vulnerable to side-channel attacks. There are some mitigated versions of AES. We evaluate \ctool{} on three variants of AES implementations: the reference implementation, the bit-sliced version, and the AES-NI implementation.
For mebedTLS, we evaluate AES-NI and the reference implementation. We do not find any leakage sites in the AES-NI version. On the other hand, the reference implementation has several leakage sites. The bit-sliced version from OpenSSL and wolfSSL should be resistant to side-channel attacks. However, we find they only adopt the protection in the encryption function but leave the key expansion function unprotected. The T-Table implementation has side-channel leakage sites in both the key expanding function and the actual encryption function.

The RSA implementations blind the secret data on a random value before operating on it. We use a fixed RSA blinding value to avoid non-deterministic behaviors during the execution. After that, we compare the result with the previous work~\cite{bao2021abacus,203878}. The result shows that \ctool{} can identify all leakage sites reported in the previous work. In addition, \ctool{} identifies new leakages in the private key decode function (\textsf{conv\_ascii2bin}) in OpenSSL 1.1.1.  To evaluate the effectiveness of the quantification result, we compare the two RSA implementations between OpenSSL 1.1.0 and OpenSSL 1.1.1.  We are interested if these leaked functions from OpenSSL 1.1.0 are fixed in OpenSSL 1.1.1.
Note that \ctool{} can analyze the side-channel leakages at both the byte granularity and the cache line granularity. We show the result analyzed with the cache line granularity.
